gradient_analysis

### 2022-10-03 ms/manuscript.Rmd
update scripts with date

---
title: "manuscript"
author: "Daniel Suh"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:   
  word_document:
    reference_docx: rv_ms_081921.docx
  pdf_document: default
bibliography: refs.bib
---

>>>>

---
title: "manuscript"
author: "Daniel Suh"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document:
    reference_docx: rv_ms_081921.docx
bibliography: refs.bib
---

### 2022-10-03 scripts/workshop/gradient_analysis.Rmd
update scripts with date

---
title: "gradient_analysis"
author: "Daniel Suh"
date: "10/30/2020"
output: html_document
---
I used this document as my instructions for most of this analysis. https://sites.ualberta.ca/~lkgray/uploads/7/3/6/2/7362679/07-gradientanalysis.pdf s

>>>>

---
title: "gradient_analysis"
author: "Daniel Suh"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---
I used this document as my instructions for most of this analysis. https://sites.ualberta.ca/~lkgray/uploads/7/3/6/2/7362679/07-gradientanalysis.pdf s
